---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bivariatechoropleths

<!-- badges: start -->
<!-- badges: end -->

The goal of **bivariatechoropleths** is to give easy and "tidy" tools for bivariate mapping, including static images for publication, dynamic maps for interactive documents, and a range of tools for creating and exploring bivariate colour palettes.

## Installation

You can install the developer version of **bivariatechoropleths** with the following command:

```{r, eval=FALSE}
devtools::install_github("chris31415926535/bivariatechoropleths")
```


## Example

Working examples will go here soon. Here's a simple call that will make an interactive bivariate choropleth using Leaflet:

```{r example, eval = FALSE}
library(bivariatechoropleths)
library(sf)

map_data <- sf::read_sf("ontario_data.shp")

leaflet::leaflet() %>%
  bivariatechoropleths::addBivariateChoropleth(map_data,
                                               variable_1,
                                               variable_2)

```

